---
title: "Aggregated Data Visualizations"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
options(digits = 3, warn = -1, max.print=50)
setwd(".")

library(plyr)
library(dplyr)
library(ggplot2)
library(extrafont)
require(reshape2)
library(nortest)
library(effsize)
library(splitstackshape)
library(car)
library(rstatix)
library(tidyverse)
library(ggpubr)
library(ez)


loadfonts()
fontSize = 10
```

### Read data

This sample contains the aggregated energy and performance measurements of 10 observations.

**Independent variables:**

1.  monitoring tool

2.  frequency

3.  workload

**Dependent variables:**

1.  energy efficiency (J)

2.  mean CPU usage percentage

3.  mean memory usage percentage

4.  total number of delivered and received datagrams

5.  duration

```{r}
data = read.csv("../data_experiment_5/data_5.csv")

data$frequency = as.factor(data$frequency)
data$workload = as.factor(data$workload)
data$tool = as.factor(data$tool)

data = rename(data, energy = energy_consumption)
data = rename(data, cpu = cpu_usage_percentage)
data = rename(data, memory = memory_usage_percentage)
data = rename(data, network = total_datagrams_count)
data = rename(data, load = load_avg)

data$run_number = as.factor(data$run_number)


data$tool <- factor(data$tool, levels = c("baseline", "elastic", "netdata", "prometheus", "zipkin"))

data$frequency = revalue(data$frequency, c("F_HIGH"="F_HIGH", "F_MEDIUM"="F_MEDIUM", "F_LOW"="F_LOW"))
data$frequency <- factor(data$frequency, levels = c("F_HIGH", "F_MEDIUM", "F_LOW"))

data$workload = revalue(data$workload, c("W_HIGH"="W_HIGH", "W_MEDIUM"="W_MEDIUM", "W_LOW"="W_LOW"))
data$workload <- factor(data$workload, levels = c("W_HIGH", "W_MEDIUM", "W_LOW"))

data$trial_id = factor(paste(data$tool, data$frequency, data$workload, sep="_"))
```

## Split data in 9 blocks

```{r}
data_f_low_w_low = data %>% filter(frequency == "F_LOW", workload == "W_LOW")
data_f_low_w_medium = data %>% filter(frequency == "F_LOW", workload == "W_MEDIUM")
data_f_low_w_high = data %>% filter(frequency == "F_LOW", workload == "W_HIGH")

data_f_medium_w_low = data %>% filter(frequency == "F_MEDIUM", workload == "W_LOW")
data_f_medium_w_medium = data %>% filter(frequency == "F_MEDIUM", workload == "W_MEDIUM")
data_f_medium_w_high = data %>% filter(frequency == "F_MEDIUM", workload == "W_HIGH")

data_f_high_w_low = data %>% filter(frequency == "F_HIGH", workload == "W_LOW")
data_f_high_w_medium = data %>% filter(frequency == "F_HIGH", workload == "W_MEDIUM")
data_f_high_w_high = data %>% filter(frequency == "F_HIGH", workload == "W_HIGH")

blocks <- list(data_f_low_w_low, data_f_low_w_medium, data_f_low_w_high, data_f_medium_w_low, data_f_medium_w_medium, data_f_medium_w_high, data_f_high_w_low, data_f_high_w_medium, data_f_high_w_high)

metrics <- c("energy", "cpu", "memory", "network", "load", "duration")

levels(data$frequency) <- c("Frequency High", "Frequency Medium", "Frequency Low")
levels(data$workload) <- c("Workload\nHigh", "Workload\nMedium", "Workload\nLow")
levels(data$tool) <- c("Baseline", "ELK stack", "Netdata", "Prometheus", "Zipkin")
```

## Visualizations

Plot global dependent variables

```{r}
fontSize = 12

bp <- ggplot(data, aes(x=tool, y=energy, fill=tool)) + #+ ylim(0, max(data$energy)) +
  geom_violin(trim = FALSE, alpha = 0.5, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("Energy (J)") +
  geom_boxplot(alpha=1, color="black", width=.2, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  theme(legend.position="none") +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp

ggsave("output/energy_global.png", scale = 1, height = 10, width = 16, unit = "cm")
```

```{r}
fontSize = 12

bp <- ggplot(data, aes(x=tool, y=duration, fill=tool)) + #+ ylim(0, max(duration)) +
  geom_violin(trim = FALSE, alpha = 0.5, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("Execution time (s)") +
  geom_boxplot(alpha=1, color="black", width=.2, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  theme(legend.position="none") +
  scale_y_continuous(breaks=seq(0, max(data$duration)+200, 120)) +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp

ggsave("output/duration_global.png", scale = 1, height = 10, width = 16, unit = "cm")
```

```{r}
fontSize = 12

bp <- ggplot(data, aes(x=tool, y=memory, fill=tool)) + #+ ylim(0, max(data$memory)) +
  geom_violin(trim = FALSE, alpha = 0.5, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("RAM usage %") +
  geom_boxplot(alpha=1, color="black", width=.2, fill="white", outlier.size=0) +
  scale_y_continuous(breaks=seq(0, 100, 10)) +
  coord_cartesian(ylim = c(0, 100)) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  theme(legend.position="none") +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp

ggsave("output/memory_global.png", scale = 1, height = 10, width = 16, unit = "cm")
```

```{r}
fontSize = 12

bp <- ggplot(data, aes(x=tool, y=cpu, fill=tool)) + #+ ylim(0, max(data$cpu)) +
  geom_violin(trim = FALSE, alpha = 0.5, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("CPU usage %") +
  geom_boxplot(alpha=1, color="black", width=.2, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point", shape=5, size=1,show.legend = FALSE) +
  scale_y_continuous(breaks=seq(0, 100, 10)) +
  coord_cartesian(ylim = c(0, 100)) +
  theme(legend.position="none") +
  guides(color=guide_legend(title="")) +    theme(strip.text.x=element_text(size=fontSize),strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp

ggsave("output/cpu_global.png", scale = 1, height = 10, width = 16, unit = "cm")
```

```{r}
fontSize = 12

bp <- ggplot(data, aes(x=tool, y=load, fill=tool)) + #+ ylim(0, max(data$load)) +
  geom_violin(trim = FALSE, alpha = 0.5, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("CPU load avg") +
  geom_boxplot(alpha=1, color="black", width=.2, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  theme(legend.position="none") +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp

ggsave("output/load_global.png", scale = 1, height = 10, width = 16, unit = "cm")
```

```{r}
fontSize = 12

bp <- ggplot(data, aes(x=tool, y=network, fill=tool)) + #+ ylim(0, max(data$network)) +
  geom_violin(trim = FALSE, alpha = 0.5, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("Total in/out datagrams") +
  geom_boxplot(alpha=1, color="black", width=.2, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  theme(legend.position="none") +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp

ggsave("output/network_global.png", scale = 1, height = 10, width = 16, unit = "cm")
```



Plot for each block.

We have 9 blocks, one for each combination of the treatments of the 2 blocking factors (frequency and workload).

```{r}
fontSize = 11

bp <- ggplot(data, aes(x=tool, y=energy, group=tool, fill=tool)) + #+ ylim(0, max(data$energy)) +
  geom_violin(trim = FALSE, alpha = 1, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("Energy (J)") +
  geom_boxplot(alpha=0.8, color="black", width=.3, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp
# bp + facet_wrap(workload ~ frequency, ncol=3, labeller = label_wrap_gen(multi_line=FALSE))
bp + facet_grid(workload ~ frequency, margin=FALSE) + theme(legend.position="none", strip.background = element_rect(
  color="white", fill="white", size=1, linetype="solid"))

ggsave("output/energy_per_blocks.png", scale = 1.6, height = 8, width = 16, unit = "cm")
```

```{r}
fontSize = 11

bp <- ggplot(data, aes(x=tool, y=network, group=tool, fill=tool)) + #+ ylim(0, max(data$network)) +
  geom_violin(trim = FALSE, alpha = 1, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("Total in/out datagrams") +
  geom_boxplot(alpha=0.8, color="black", width=.3, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point", shape=5, size=1,show.legend = FALSE) +
  guides(color=guide_legend(title="")) +
  theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp
# bp + facet_wrap(workload ~ frequency, ncol=3, labeller = label_wrap_gen(multi_line=FALSE))
bp + facet_grid(workload ~ frequency, margin=FALSE) + theme(legend.position="none", strip.background = element_rect(
  color="white", fill="white", size=1, linetype="solid"))

ggsave("output/network_per_blocks.png", scale = 1.6, height = 8, width = 16, unit = "cm")
```

```{r}
fontSize = 11

bp <- ggplot(data, aes(x=tool, y=memory, group=tool, fill=tool)) + #+ ylim(0, max(data$memory)) +
  geom_violin(trim = FALSE, alpha = 1, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("RAM usage %") +
  geom_boxplot(alpha=0.8, color="black", width=.3, fill="white", outlier.size=0) +
  scale_y_continuous(breaks=seq(0, 100, 20)) +
  coord_cartesian(ylim = c(0, 100)) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp
# bp + facet_wrap(workload ~ frequency, ncol=3, labeller = label_wrap_gen(multi_line=FALSE))
bp + facet_grid(workload ~ frequency, margin=FALSE) + theme(legend.position="none", strip.background = element_rect(
  color="white", fill="white", size=1, linetype="solid"))

ggsave("output/memory_per_blocks.png", scale = 1.6, height = 8, width = 16, unit = "cm")
```

```{r}
fontSize = 11

bp <- ggplot(data, aes(x=tool, y=cpu, group=tool, fill=tool)) + #+ ylim(0, max(data$cpu)) +
  geom_violin(trim = FALSE, alpha = 1, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("CPU usage %") +
  geom_boxplot(alpha=0.8, color="black", width=.3, fill="white", outlier.size=0) +
  scale_y_continuous(breaks=seq(0, 100, 20)) +
  coord_cartesian(ylim = c(0, 100)) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp
# bp + facet_wrap(workload ~ frequency, ncol=3, labeller = label_wrap_gen(multi_line=FALSE))
bp + facet_grid(workload ~ frequency, margin=FALSE) + theme(legend.position="none", strip.background = element_rect(
  color="white", fill="white", size=1, linetype="solid"))

ggsave("output/cpu_per_blocks.png", scale = 1.6, height = 8, width = 16, unit = "cm")
```

```{r}
fontSize = 11

bp <- ggplot(data, aes(x=tool, y=load, group=tool, fill=tool)) + #+ ylim(0, max(data$load)) +
  geom_violin(trim = FALSE, alpha = 1, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("CPU load avg") +
  geom_boxplot(alpha=0.8, color="black", width=.3, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp
# bp + facet_wrap(workload ~ frequency, ncol=3, labeller = label_wrap_gen(multi_line=FALSE))
bp + facet_grid(workload ~ frequency, margin=FALSE) + theme(legend.position="none", strip.background = element_rect(
  color="white", fill="white", size=1, linetype="solid"))

ggsave("output/load_per_blocks.png", scale = 1.6, height = 8, width = 16, unit = "cm")
```

```{r}
fontSize = 11

bp <- ggplot(data, aes(x=tool, y=duration, group=tool, fill=tool)) + #+ ylim(0, max(data$duration)) +
  geom_violin(trim = FALSE, alpha = 1, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("Execution time (s)") +
  geom_boxplot(alpha=0.8, color="black", width=.3, fill="white", outlier.size=0) +
  scale_y_continuous(breaks=seq(0, max(data$duration)+200, 120)) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
bp
# bp + facet_wrap(workduration ~ frequency, ncol=3, labeller = label_wrap_gen(multi_line=FALSE))
bp + facet_grid(workload ~ frequency, margin=FALSE) + theme(legend.position="none", strip.background = element_rect(
  color="white", fill="white", size=1, linetype="solid"))

ggsave("output/duration_per_blocks.png", scale = 1.6, height = 8, width = 16, unit = "cm")
```

Plot for each block + global

```{r}
bp <- ggplot(data, aes(x=tool, y=energy, group=tool, fill=tool)) + #+ ylim(0, max(data$energy)) +
  geom_violin(trim = FALSE, alpha = 0.5, position=position_dodge(0.9)) + theme_bw() + xlab("Tools") + ylab("Energy (J)") +
  geom_boxplot(alpha=1, color="black", width=.2, fill="white", outlier.size=0) +
  stat_summary(fun=mean, colour="black", geom="point",
               shape=5, size=1,show.legend = FALSE) +
  guides(color=guide_legend(title="")) + theme(strip.text.x=element_text(size=fontSize), strip.text.y=element_text(size=fontSize),  axis.text.x=element_text(size=fontSize, angle = 45, hjust = 1), axis.text.y=element_text(size=fontSize), axis.title=element_text(size=fontSize))
# + geom_jitter(shape=16, size = 0.5, position=position_jitter(0.2))
bp
# bp + facet_wrap(environment ~ movement, ncol=3, labeller = label_wrap_gen(multi_line=FALSE))
bp + facet_grid(workload ~ frequency, margin=TRUE) + theme(legend.position="none", strip.background = element_rect(
  color="white", fill="white", size=1, linetype="solid"))

ggsave("output/energy_per_block_large.png", scale = 1.6, height = 15, width = 24, unit = "cm")
```


Plot correlation

Duration vs Energy

```{r}
# create multiple linear model
lm_fit <- lm(duration ~ energy, data=data)
summary(lm_fit)

# save predictions of the model in the new data frame
# together with variable you want to plot against
predicted_df <- data.frame(mpg_pred = predict(lm_fit, data), hp=data$energy)

# this is the predicted line of multiple linear regression
ggplot(data = data, aes(x = duration, y = energy, color=tool)) +
  labs(title = "", x = "Execution time (s)",  y = "Energy (J)", color="Tool") +
  scale_x_continuous(breaks=seq(0, max(data$duration), 60)) +
  geom_point() +
  geom_line(color='red',data = predicted_df, aes(x=mpg_pred, y=hp))  + 
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
      legend.position = "none",
      strip.background = element_rect(color="white", fill="white", size=1, linetype="solid"),
      panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "#EBE5E3"),
      panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "#EBE5E3"))

cor(data$cpu, data$energy,method="spearman")
cor(data$load, data$energy,method="spearman")
cor(data$memory, data$energy,method="spearman")
cor(data$duration, data$energy,method="spearman")
cor(data$network, data$energy,method="spearman")

ggsave("output/duration_energy.png", scale = 1, height = 7, width = 16, unit = "cm")
```
```{r}
# create multiple linear model
lm_fit <- lm(memory ~ energy, data=data)
summary(lm_fit)

# save predictions of the model in the new data frame
# together with variable you want to plot against
predicted_df <- data.frame(mpg_pred = predict(lm_fit, data), hp=data$energy)

# this is the predicted line of multiple linear regression
ggplot(data = data, aes(x = memory, y = energy, color=tool)) +
  labs(title = "", x = "RAM usage %",  y = "Energy (J)", color="Tool") +
  scale_x_continuous(breaks=seq(0, 100, 10)) +
  coord_cartesian(xlim = c(0, 100)) +
  geom_point() +
  geom_line(color='red',data = predicted_df, aes(x=mpg_pred, y=hp))  + 
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
      legend.position = "none",
      strip.background = element_rect(color="white", fill="white", size=1, linetype="solid"),
      panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "#EBE5E3"),
      panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "#EBE5E3"))

ggsave("output/ram_energy.png", scale = 1, height = 7, width = 16, unit = "cm")
```

```{r}
# create multiple linear model
lm_fit <- lm(cpu ~ energy, data=data)
summary(lm_fit)

# save predictions of the model in the new data frame
# together with variable you want to plot against
predicted_df <- data.frame(mpg_pred = predict(lm_fit, data), hp=data$energy)

# this is the predicted line of multiple linear regression
ggplot(data = data, aes(x = cpu, y = energy, color=tool)) +
  labs(title = "", x = "CPU usage %",  y = "Energy (J)", color="Tool") +
  scale_x_continuous(breaks=seq(0, 100, 10)) +
  coord_cartesian(xlim = c(0, 100)) +
  geom_point() +
  geom_line(color='red',data = predicted_df, aes(x=mpg_pred, y=hp)) + 
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
      legend.position = "none",
      strip.background = element_rect(color="white", fill="white", size=1, linetype="solid"),
      panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "#EBE5E3"),
      panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "#EBE5E3"))

ggsave("output/cpu_energy.png", scale = 1, height = 7, width = 16, unit = "cm")
```
```{r}
# create multiple linear model
lm_fit <- lm(load ~ energy, data=data)
summary(lm_fit)

# save predictions of the model in the new data frame
# together with variable you want to plot against
predicted_df <- data.frame(mpg_pred = predict(lm_fit, data), hp=data$energy)

# this is the predicted line of multiple linear regression
ggplot(data = data, aes(x = load, y = energy, color=tool)) +
  labs(title = "", x = "CPU load avg",  y = "Energy (J)", color="Tool") +
  geom_point() +
  geom_line(color='red',data = predicted_df, aes(x=mpg_pred, y=hp)) + 
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
      legend.position = "none",
      strip.background = element_rect(color="white", fill="white", size=1, linetype="solid"),
      panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "#EBE5E3"),
      panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "#EBE5E3"))

ggsave("output/load_energy.png", scale = 1, height = 7, width = 16, unit = "cm")
```
```{r}
# create multiple linear model
lm_fit <- lm(network ~ energy, data=data)
summary(lm_fit)

# save predictions of the model in the new data frame
# together with variable you want to plot against
predicted_df <- data.frame(mpg_pred = predict(lm_fit, data), hp=data$energy)

# this is the predicted line of multiple linear regression
ggplot(data = data, aes(x = network, y = energy, color=tool)) +
  labs(title = "", x = "Total in/out datagrams",  y = "Energy (J)", color="Tool") +
  geom_point() +
  scale_color_hue(labels = c("Baseline", "ELK stack", "Netdata", "Prometheus", "Zipkin")) +
  geom_line(color='red',data = predicted_df, aes(x=mpg_pred, y=hp))  + 
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
      legend.position = "bottom",
      strip.background = element_rect(color="white", fill="white", size=1, linetype="solid"),
      panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "#EBE5E3"),
      panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "#EBE5E3"))

ggsave("output/network_energy.png", scale = 1, height = 10, width = 16, unit = "cm")
```